Communication complexity: Chapter 4 \\ Randomized communication complexity

### 2019-02-01 CS860-CommunicationComplexity/assignments/Chapter4.tex
bonus

>>>>

\begin{proof}
Consider a public-coin randomized protocol $\pi$ attaining cost $R_\epsilon(f)$. Let $t = 2n/\epsilon^2$ and consider $\pi$ run on $t$ random strings $r_1, \dots, r_t$ drawn independently at random. Fix an input $(x,y) \in \calX \times \calY$. For any $i \in [t]$, the probability that $\pi$ fails when run on $r_i$ is at most $\epsilon$.
Hence the probability that $(1-2\epsilon)t$ strings amongst $r_1, \dots, r_t$ fail when $\pi$ runs using that string is at most
$$2^{-\Omega(\epsilon^2t)} = 2^{-\Omega(2n)}$$
by Chernoff Bounds.

Now, by the union bound, for any input in $\calX\times \calY$ the probability that greater than $2\epsilon t$ strings fail when $\pi$ runs them is strictly less than $1$. Thus, by the probabilistic method there exist strings $R = \{r_1^*, \dots, r_t^*\}$ with the property that for any input pair at most $2\epsilon t$ strings in $R$ fail when $\pi$ runs using that string.

Our private coin protocol is as follows. Alice samples a string $r_i^* \in R$ uniformly at random, and sends its index $i$ to Bob. This costs $O(\log\frac{n}{\epsilon^2})$ communication. Now they can use $r_i^*$ as a source of shared randomness to run $\pi$ at additional communication cost $R_\epsilon(f)$. Since at most $2\epsilon t$ string in $R$ fail, the probability of failure for this protocol is at most
$$2\epsilon t/t = 2\epsilon$$
as desired.
\end{proof}
